%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% * <coldblood0112@gmail.com> 2017-08-30T16:49:40.959Z:
%
% ^.
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% * <coldblood0112@gmail.com> 2017-08-30T16:50:06.561Z:
%
% ^.
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, ]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Abhinandan Dutt} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{V.P.O. Pragpur, Teh. Dehra} % Your address
\moveleft.5\hoffset\centerline{Kangra, Himachal Pradesh(177107)}
\moveleft.5\hoffset\centerline{+91-7085850396}
\moveleft.5\hoffset\centerline{duttabhinandan1996@gmail.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{OBJECTIVE}  

A place where I can use all my knowledge, skills and thoughts to give maximum production and gain maximum coverage to my present tendencies in my field in this manner to attaining my goals both as a professional and organizational 


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}
\textbf{University of Technology and Management}\hfill August 2014 - June 2018\\
{\sl Pursuing Bachelor of Technology Computer Science\\ 
specialization in Oil \& Gas Informatics}  \hfill CGPA : 2.41/4 \\


\textbf{D.A.V. Senior Secondary Public School, } Dehra, Himachal Pradesh\\
{\sl Class XII }, CBSE Board, 2014 \hfill
Percentage : 66\%

\textbf{Kendriya Vidyalaya, } Naleti, Himachal Pradesh \\
{\sl Class X }, CBSE Board, 2012 \hfill
CGPA : 7.4



%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY \\ SKILLS} 

{\sl Programming Languages:} Java, C++ \\
{\sl Web Backend Technologies:} MySQL \\
{\sl Scripting language:} PHP \\
{\sl Framework:} Codeigniter \\
{\sl Development stack:} XAMP \\

 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{PROJECT EXPERIENCE}

{\sl Routing Algorithm} \hfill August 2016 - November 2016 \\

\begin{itemize}
\item It is a desktop based application which used Java.
\item The project is about learning and understanding how routing works and what are its benefits 
\item Use of multiple routing algorithm to find which is efficient and faster in multiple conditions. 

\end{itemize} 
{\sl To-Dos} \hfill January 2017 - May 2017 \\
\begin{itemize}
\item To-Dos is the project name.
\item To-dos is a small web based application which allows user to save important notes and tasks.
\item To-dos uses username and password to login and let user save its data.
\item There are for main roles in the system, Create to-do, Delete to-do, Show to-do, Patch to-do.
\item Technologies which are being used to developed this web application are Node.js, postman to interface, Mango DB as database.
\end{itemize}

\section{INDUSTRIAL TOUR}

{\sl IBM} \hfill 10th FEBRUARY 2017 , 14th FEBRUARY 2017

\begin{itemize}
\item Learn about IBM bluemix, watson, blockchain and visited IBM data centre.
\end{itemize} 

{\sl TARGET CORPORATION} \hfill 15th FEBRUARY 2017

\begin{itemize}
\item Learn about the target corporation and how Indian teams are integrated with team in United States.
\end{itemize} 
{\sl STPI} \hfill 16th FEBRUARY 2017

\begin{itemize}
\item Learn about the UPI and how to use BHIM application developed by NPCI.
\end{itemize} 

\section{INTERNSHIP}

{\sl Shanrohi Technologies PVT LIMITED} \hfill 1th JUNE 2017 - 31st JULY 2017

\begin{itemize}
\item The Project was to develop a website "Fixcars.co" for vehicle Servicing.
\item It was developed using technologies like PHP, codeigniter Framework, HTML, javascript, CSS, Bootstrap, json, and MySQl as database.
\end{itemize} 

%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%---------------------------------------------------------------------------------------- 


%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%--------------------------------------------------------------------------https://preview.overleaf.com/public/jhfsdvgkydvb/images/11b5fe13113e160e7917f614d3fc9dd01deaa79c.jpeg--------------

\section{CO-CURRICULAR \\ ACTIVITIES} 
\begin{itemize}

\item Industrial Automation PLC and SCADA of duration 2 days, Workshop organized by Technex 16, IIT Varanasi, February 22 and 23, 2016.

\item Basics of Crude Oil, Refining Processes, Digital Oil Fields organized Webinar IBM on 30, March, 2016

\item University Basketball Championship(Runner-up) 2017

\end{itemize}
 

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}